Syntax and Semantics of Cedille

### 2020-10-18 docs/semantics/arxiv-version.tex
docs: update arxiv version

Defining \verb|Top| to be $\{\absu{\lambda}{x}{x} \simeq
\absu{\lambda}{x}{x}\}$, we may assign \verb|Top| to any closed term \verb|t|,
including non-normalizing ones.  In our annotated syntax, we write \verb|β{t}|.
Even without this, the presence of
$\delta$ in combination with $\phi$ allows us to type non-normalizing
terms assuming an erased argument $x$ of type $\{ \textit{tt} \simeq
\textit{ff} \}$ for Church-encoded booleans \textit{tt} and
\textit{ff}.  For example, $\delta\ \mhyph x$ has type
\verb|{λ x . x ≃ λ x . x x}|, and with $\phi$ we can use this to type
$\Omega$ by changing the typed term \verb|id · True id|, where
\verb|True| is \verb|∀ X : ★ . X ➔ X|. But failure of normalization
does not impinge on Theorem~\ref{thm:consis}.   Extensional Martin-L\"of type theory (MLTT) is
also non-normalizing, for a very similar reason, but this fact
does not contradict its logical soundness~\cite{dybjer16}.  In CDLE, the guarantees one gets about the
behavior of terms are expressed almost entirely in their types.  If
the types are weak, then not much is guaranteed; but stronger types
can guarantee properties like normalization, as demonstrated by the following
theorem:

@@

>>>>

Defining \verb|Top| to be $\{\absu{\lambda}{x}{x} \simeq
\absu{\lambda}{x}{x}\}$, we may assign \verb|Top| to any closed term \verb|t|,
including non-normalizing ones. In our annotated syntax, we write
\texttt{\(\beta\)\{t\}}. Even without this, the presence of $\delta$ in
combination with $\phi$ allows us to type non-normalizing terms assuming an
erased argument $x$ of type $\{ \textit{tt} \simeq \textit{ff} \}$ for
Church-encoded booleans \textit{tt} and \textit{ff}. For example, $\delta\ \mhyph x$
has type \(\{\absu{\lambda}{x}{x} \simeq \absu{\lambda}{x}{x\ x}\}\), and with
$\phi$ we can use this to type $\Omega$ by changing the typed term
\(\texttt{id}\ \cdot\texttt{True}\ \texttt{id}\), where \verb|True| is
\(\abs{\forall}{X}{\star}{X \to X}\). But failure of normalization does not
impinge on Theorem~\ref{thm:consis}. Extensional Martin-L\"of type theory (MLTT)
is also non-normalizing, for a very similar reason, but this fact does not contradict
its logical soundness~\cite{dybjer16}. In CDLE, the guarantees one gets about
the behavior of terms are expressed almost entirely in their types. If the types
are weak, then not much is guaranteed; but stronger types can guarantee
properties like normalization, as demonstrated by the following theorem:

@@

\bibitem{Kashima2000}
  Ryo Kashima.
  \newblock {A Proof of the Standardization Theorem in \(\lambda\)-Calculus}.
  \newblock Available from the author's web page, 2000.
